Figures

### 2019-06-24 figures/07_model-selection.Rmd
plot ndep vs re slope

plot_grid(gg_hist, gg_tp, nrow = 2)
```

>>>>

plot_grid(gg_hist, gg_tp, nrow = 2)

lg <- lagosne_load("1.087.1")
gg_line <- fit_tn$re %>%
  ungroup() %>%
  mutate(hu4vzoneid = paste0("HU4_", hu4vzoneid)) %>%
  left_join(dplyr::select(lg$hu4.chag, 
                          hu4_zoneid, hu4_dep_totaln_2010_mean), 
            by = c("hu4vzoneid" = "hu4_zoneid")) %>%
ggplot() +
  geom_point(aes(x = hu4_dep_totaln_2010_mean, y = `50%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  theme_cowplot() +
  ylab("TN model, corn RE slope") + xlab("N deposition") +
  theme(legend.position = 0)

gg_tn_re
